\chapter{Introduction}

\section{Motivation}

The rapid evolution of Artificial Intelligence (AI) has fundamentally change the global socio-economic landscape. To adapt to the new era, self\-studying and learning method are becoming more and more important. Traditional education philosophy, such as "practice makes perfect," has no longer been the absolute true; when AI can automate execution, the value of learning moves from procedural fluency and labour expertise to conceptual mastery and strategic analysis. However, current education system fail to keep pace with this evolution:

\begin{itemize}
    \item \textbf{Stagnancy of Content:} Legacy Learning Management Systems (LMS) treat knowledge as static artifacts (textbooks, slides). These materials fail to adapt to the varying cognitive baselines of individual students.
    \item \textbf{The Guidance Deficit:} Without a dynamic roadmap, students navigate a "sea of information" where external resources are either too granular (leading to information overload) or too condensed (creating knowledge gaps), with little profound ground truth.
    \item \textbf{The Lack of Interaction:} Current systems lack a feedback loop. Textbooks exceed the average human attention span, while slides provide too condensed context insufficient for novices, leaving no room for real-time, human-like inquiry or mentorship.
    \item \textbf{Outdated Knowledge:} Educational materials and methods cannot catch up with the change of technology. Internet are an invaluable resource, however information is chaotic, unstructured and content are confusing to many new learners.
\end{itemize}

While Large Language Models (LLMs) offer a glimpse into automated resource synthesis and knowledge base construction, significant technical bottleneck prevent their reliable application in complex domains:

\begin{itemize}
    \item \textbf{Semantic Fragmentation in RAG:} Traditional Retrieval-Augmented Generation (RAG) frameworks rely on discrete data chunking. This fragmentation disrupts the global structural integrity of a subject, leading to "contextual myopia" where the model captures isolated facts but fails to comprehend the overarching hierarchy of the domain.
    \item \textbf{Contextual Saturation vs. Precision:} Expanding the context window of LLMs often introduces diminishing returns. The injection of unrefined data frequently leads to "contextual overhead" and "noise," where the model struggles to distinguish fundamental principles from peripheral details.
    \item \textbf{Relational Limitations of Vector Space:} Relying exclusively on vector embeddings (typically $\approx 1024$ dimensions) is insufficient for mapping the non-linear, multi-faceted dependencies inherent in academic taxonomies. Similarity-based retrieval cannot substitute for the deterministic logic required to understand prerequisite relationships.
    \item \textbf{The Reasoning Gap in Pedagogy:} Instruction is a sophisticated, non-linear reasoning task. Current AI systems are largely reactive—proficient in text generation but deficient in long-term goal tracking and proactive guidance. This results in a susceptibility to hallucinations and an inability to execute the "evaluate-and-guide" workflow essential for effective pedagogy.
\end{itemize}

\section{Goals}\label{sec:goal}

To address the current limitations, this project aims to design an Intelligent System far beyond serving contents or a simple QA chatbot: a proactive, mastery-oriented 
learning platform tracking and adapting to student progress by developing \textbf{SmartEdu}—an intelligent, graph-grounded 
educational ecosystem.. This thesis determined for such a system which capabilities include:

\begin{itemize}
    \item \textbf{Adaptive Mentorship:} Shifting the educational paradigm from static, linear content delivery systems to an interactive, human-like mentorship 
    that dynamically reform itself based on student performance.
    \item \textbf{Data Sovereignty and Localized Execution:} Establishing a sustainable deployment framework that leverages open-weights Small Language Models 
    (SLMs) and local inference engines, ensuring complete data privacy for student learning behaviors while eliminating recurring API token costs.
    \item \textbf{Consistent Educational Contents:} Intelligent contents adaptation and generation suffers from hallucinations and key info lost. Mitigating the 
    hallucination risks inherent in generative AI by anchoring the multi-agent reasoning framework within a 
    structured knowledge network to enforce academic truthfulness.
\end{itemize}

Targeted at University students, this educational platform facilitates student self learning, the most important skills in University. 
To demonstrate practical utility and fulfill the discussed goals of an actionable software solution, the application indentifies the following 
key features:
\begin{itemize}
    \item \textbf{Automated Educational Knowledge Graph (EKG) Engine:} The system automatically ingests unstructured academic materials 
    (raw PDFs, textbooks, and lecture videos) and constructs a structured knowledge graph. It automatically extracts conceptual hierarchies, 
    maps prerequisite dependencies, and group related topics into organized clusters.
    \item \textbf{Dynamic Student Mastery Mapping:} The application implements a continuous storing-and-tracking engine that tracks the student's real-time 
    comprehension levels, storing historical interaction and cognitive progress securely.
    \item \textbf{Automated Gap Detection and Pathfinding:} Leveraging graph-traversal and heuristic algorithms, the system choose a good studying path based on 
    the student's current mastery and state against the EKG backbone. When a target topic is selected, the application automatically identifies missing prerequisite 
    knowledge and dynamically generates a personalized, non-linear learning path.
    \item \textbf{Socratic Dialogue and Document Verification:} The user interface provides an interactive teaching assistant that engages students using powerfull 
    reasoning workflow.
\end{itemize}

\section{Scope}

To fulfill these goals, the research focuses on the following researching scope:
\begin{itemize}
    \item \textbf{Multimodal Information Extraction:} Knowledge of courses from multiple sources (pdf, videos, textbooks) must be well extracted 
    to consolidate them into a centralized data repository.
    \item \textbf{Domain Specificity:} The knowledge modeling and extraction processes are limited to well-defined academic disciplines with clear hierarchical structures. Unstructured or subjective domains that lack clear prerequisite dependencies are outside the scope of this research.
    \item \textbf{Pedagogical Boundaries:} The conversational assistant is strictly restricted to goal-oriented educational support, specifically for assessing 
    student understanding and explaining course content. Open-domain dialogue, creative writing, and casual chitchat are intentionally disabled.
    \item \textbf{Infrastructure:} The system optimizes execution using open-weights models to maintain strict data privacy. 
    \item \textbf{Target User Environment:} The system is modeled and evaluated for a single-institution environment, focusing on the interactions between individual learners and a localized knowledge base, rather than a multi-tenant, global-scale educational network.
\end{itemize}
There are 7 chapters in this project's report:

\begin{itemize}
    \item \textbf{Chapter 1} introduces the problems, proposes the system's goals, scopes and thesis structure
    \item \textbf{Chapter 2} provides fundamental knowledge for project understand and deep literature review of relevant prior researches covering topic, as well as preview of open-source application.
    \item \textbf{Chapter 3} Requirement Specifications
    \item \textbf{Chapter 4} propose methodologies: we discuss what inferred from previous work and what ways to solve the specific usecase of ours
    \item \textbf{Chapter 5} details the system including: System architecture and its components, settings in each components, and finally, their implementation explanation that fully illustrate how do the system put proposed methodology to practice 
    \item \textbf{Chapter 6} analyzes the system outcomes from components to final output as a whole
    \item \textbf{Chapter 7} is the conclusion to the result: what the system achieved, its limitation and future improvements for the final Capstone Project
\end{itemize}