\chapter{Requirements Specifications}\label{chap:req}

The limitations discussed in Subsection~\ref{sub:gaps} have shaped the technical vision for the proposed system. To address these gaps and deliver a robust, 
scalable educational platform following our goal (Section~\ref{sec:goal}), this section outlines the explicit Functional and Non-Functional Requirements, as well as 
visiallizing use---case design. These requirements are derived directly from the systemic constraints and the pedagogical needs of learners for a more personalized, 
diversed and comprehensive learning assistance system.

\section{Functional Requirements}\label{sec:fun}

\subsection{Knowledge Modelling and Management}
As a key objective feature, knowledge modelling construct knowledge base, foundation to all other key features. This functional category encompasses the capabilities 
required to process raw educational inputs into a structured knowledge base.

\begin{itemize}
    \item \textbf{Data Ingestion and Parsing:} 
    \begin{itemize}
        \item The system must be able to ingest unstructured, text-dense academic formats (e.g., PDF textbooks, syllabus guidelines).
        \item The system must accurately parse text into discrete chunks while retaining crucial positional metadata (e.g., source file origin, exact page numbers).
    \end{itemize}
    
    \item \textbf{Semantic Extraction and Normalization:}
    \begin{itemize}
        \item The system must extract fundamental educational concepts and their explicit pedagogical relationships from the ingested text.
        \item The system must normalize extracted entities to a canonical form to ensure conceptual consistency and prevent any form of semantic fragmentation (even of different course) 
        across the knowledge base.
    \end{itemize}
    
    \item \textbf{Hierarchical and Relational Organization:}
    \begin{itemize}
        \item The system must organize extracted entities into a standardized hierarchical topology.
        \item The system must automatically group highly related concepts into cohesive educational clusters or chapters.
        \item The system must explicitly define and store directional "prerequisite" relationships between concepts to enable automated learning path generation.
    \end{itemize}
    
    \item \textbf{Storage Capability:}
    \begin{itemize}
        \item The persistence mechanism must guarantee a database structure that facilitates high-speed, complex relational querying and subgraph retrieval during live 
        interactions.
        \item To ensure diversity of learning input, storage design must ensure efficient storing of enormous data with reasonable latency. 
    \end{itemize}
\end{itemize}

\subsection{Intelligent Teaching Assistance}
To utilized modeled knowledge base as well as guarantee satisfactory learning experience and result, the design of agentic system that serves as our Teaching Assistance 
is crucial. This category defines the required behaviors and reasoning capabilities of the automated teaching assistant.

\begin{itemize}
    \item \textbf{Intent Recognition and Context Orchestration:}
    \begin{itemize}
        \item The system must classify user intents (e.g., Retrieve information, Generate roadmap, Clarify concepts) and autonomously route the request to the appropriate internal workflow.
        \item The system must dynamically gather necessary context before responding, which includes retrieving the student's personal mastery history and the relevant subset of the educational knowledge base.
    \end{itemize}
    
    \item \textbf{Intelligent Reasoning and Supervision:}
    \begin{itemize}
        \item The system must support a Socratic teaching interaction; it must be capable of generating probing questions to assess student comprehension 
        rather than merely providing direct answers.
        \item The system must objectively evaluate the student's response to determine whether to authorize progression to the next prerequisite topic.
        \item The system must be able to autonomously detect when it lacks sufficient context to answer a question and execute a fallback strategy that 
        synthesizes information from the broader knowledge base.
    \end{itemize}
    
    \item \textbf{Response Verifiability and Fallback:}
    \begin{itemize}
        \item To guarantee grounded responses, the system must prioritize explicit document referencing, citing exact source pages for its generated answers.
        \item The system must execute a broader knowledge synthesis fallback only when direct contextual concepts are missing from the immediate document.
    \end{itemize}
\end{itemize}

\subsection{Student Interaction and System Navigation}
This category defines the functional requirements concerning the end-user's experience, accessibility, and direct interaction with the intelligent system.

\begin{itemize}
    \item \textbf{Identity and Access Security:}
    \begin{itemize}
        \item The system must provide secure authentication capabilities (Login/Logout) to uniquely identify users.
        \item The system must maintain isolated, tamper-proof session states for each user to securely record individual learning progress without cross-user data exposure.
    \end{itemize}
    
    \item \textbf{Interactive Dialogue and Visualization:}
    \begin{itemize}
        \item The system must provide a natural language chat interface that supports continuous, multi-turn conversational interactions and real-time streaming responses.
        \item The system must dynamically render visual learning roadmaps, empowering students to make informed, user-centric choices regarding their educational progression rather than following a static curriculum.
        \item The interface must consolidate essential learning tools, providing seamlessly integrated functional components such as conversational history logs, a synchronized document viewer, and progress summarization dashboards.
    \end{itemize}
    
    \item \textbf{Advanced Navigation and Content Discovery:}
    \begin{itemize}
        \item The system must implement an intuitive, multi-level navigation structure (e.g., breadcrumb trails) to help students orient themselves within complex knowledge hierarchies.
        \item The system must incorporate a powerful semantic search utility, allowing users to rapidly query and locate specific educational materials, graph concepts, or historical interactions.
    \end{itemize}
    
    \item \textbf{Contextual and Responsive Feedback:}
    \begin{itemize}
        \item The system must be capable of emitting explicit interface triggers alongside its textual responses to automatically synchronize the user's interface (e.g., auto-scrolling the document viewer to the exact referenced page).
        \item Notifications and intelligent pedagogical prompts must be delivered in a non-intrusive, accessible manner that captures user attention while preserving the fluidity of the learning experience.
    \end{itemize}
\end{itemize}


\section{Non-Functional Requirements}\label{sec:nonfun}
To create a powerful, reliable, and user-friendly educational platform, the Smart Learning System cannot stop at being functional, but need focusing on efficiency 
and overall system performance. Thus, it must also adhere to a set of non-functional requirements that govern its 
performance, scalability, security, and overall user experience.
\begin{itemize}
    \item \textbf{Scalability and Modularity:}
    \begin{itemize}
        \item The backend architecture must be designed as stateless, relying exclusively on external persistence layers for state management to ensure readiness 
        for future distributed scaling.
        \item System design must be modular, with clear separation of components reponsibility and dependency to facilitate future enhancements, maintenance, and potential integration of 
        additional features or third-party services.
    \end{itemize}

    \item \textbf{Resource Optimization and Latency Minimization:}
    \begin{itemize}
        \item Operating under the constraint of localized execution, the system must optimize memory and computational overhead, loading resource-heavy 
        models into memory only when explicitly demanded by an active workflow.
        \item All resource must be efficiently released immediately after use to minimize the system's memory footprint and ensure responsiveness.
        \item System must be scheduled to be constantly running, minimizing downtime and waiting time for any task.
        \item All resource must be managable, specifically for developers and system administrators, but crucial for maintaining system stability and performance.
    \end{itemize}

    \item \textbf{Reliability and Determinism:}
    \begin{itemize}
        \item The system must mitigate the inherent unpredictability of generative AI by enforcing strict, programmatic data schemas for all internal system communications and decision-making logic.
        \item Complex analytical tasks, such as calculating knowledge gaps, must be executed via deterministic programmatic logic rather than relying on probabilistic generative approximations.
    \end{itemize}

    \item \textbf{Observability and Traceability:}
    \begin{itemize}
        \item The system must maintain comprehensive telemetry across all automated workflows.
        \item Database state changes, including knowledge graph updates and student progress logs, must be monitored and saved to enable historical analysis and rollback capabilities.        
        \item Every automated decision, context retrieval action, and resource consumption metric must be actively logged to provide a transparent audit trail for both system debugging and pedagogical evaluation.
    \end{itemize}
    \item \textbf{User Experience and Interface Requirements:}
    \begin{itemize}
        \item User interface is focus on the simplicity and intuitiveness, ensuring that users of varying technical proficiency can navigate the system effectively.
        \item User interface must be responsive and accessible, adhering to modern web standards to ensure compatibility across a wide range of devices and screen sizes (phones, tablets, desktops).
        \item Client side shouldn't be pulled by heavy backend response latency. It should maintain a fluid, real-time interaction experience, minimizing latency 
        in response generation and interface updates. Mininizing \texttt{"user experience latency"} regardless of system performance 
        is a strategic design move to preserve conversational engagement as well as learning interest.
    \end{itemize}

\end{itemize}




\section{Use Cases}\label{sec:usecase}

\subsection{Use case 1: Register Account}
\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.5}
    \begin{tabularx}{\textwidth}{|l|X|}
        \hline
        \textbf{Use Case Name} & Register Account \\
        \hline
        \textbf{Actor} & User (Student) \\
        \hline
        \textbf{Description} & The user registers a new account in the system to access personalized learning features. \\
        \hline
        \textbf{Preconditions} & The user does not already have an account with the chosen student ID/username. \\
        \hline
        \textbf{Postconditions} & A new user account is successfully created in the database. \\
        \hline
        \textbf{Normal Flow} & 
        1. User are navigated to the registration page.\newline
        2. User enters student ID and password.\newline
        3. System validates that the student ID is not already taken.\newline
        4. System creates the account and securely stores credentials.\newline
        5. User is redirected to the login page. \\
        \hline
        \textbf{Alternative Flow} & 
        \textbf{Username taken:}\newline
        A1. User submits an already registered student ID.\newline
        A2. System displays an error message asking the user to choose another ID or log in. \\
        \hline
        \textbf{Exceptions} & If the backend database is unreachable, show a ``Service temporarily unavailable'' message. \\
        \hline
    \end{tabularx}
    \caption{Use case 1 Overview: Register Account}\label{tab:uc1}
\end{table}

\subsection{Use case 2: Login/Logout}
\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.5}
    \begin{tabularx}{\textwidth}{|l|X|}
        \hline
        \textbf{Use Case Name} & Login/Logout \\
        \hline
        \textbf{Actor} & User \\
        \hline
        \textbf{Description} & The user logs in to the system to access authorized features and logs out to end the session. \\
        \hline
        \textbf{Preconditions} & The user has a valid account.\newline
        The system is connected to the authentication service. \\
        \hline
        \textbf{Postconditions} & User is successfully logged in (receiving a valid access token) or logged out. \\
        \hline
        \textbf{Normal Flow} & 
        \textbf{Login:}\newline
        1. User navigates to the login page.\newline
        2. User enters username and password.\newline
        3. System validates credentials and generates JWT token.\newline
        4. User is redirected to the dashboard/homepage.\newline
        \textbf{Logout:}\newline
        5. User clicks the logout button.\newline
        6. System clears the session token and redirects to the login page. \\
        \hline
        \textbf{Alternative Flow} & 
        \textbf{Invalid login attempt:}\newline
        A1. User submits incorrect credentials.\newline
        A2. System displays an error message and asks user to retry. \\
        \hline
        \textbf{Exceptions} & If the authentication service is unavailable, show a ``Service temporarily unavailable'' message. \\
        \hline
    \end{tabularx}
    \caption{Use case 2 Overview: Login/Logout}\label{tab:uc2}
\end{table}

\subsection{Use case 3: Manage Learning Session}
\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.5}
    \begin{tabularx}{\textwidth}{|l|X|}
        \hline
        \textbf{Use Case Name} & Manage Learning Session \\
        \hline
        \textbf{Actor} & User (Student) \\
        \hline
        \textbf{Description} & The user starts a new learning session to begin interacting with the curriculum, and ends it upon finishing. \\
        \hline
        \textbf{Preconditions} & The user is logged in and authenticated. \\
        \hline
        \textbf{Postconditions} & A unique session state is initialized or terminated for tracking the student's progress and history. \\
        \hline
        \textbf{Normal Flow} & 
        \textbf{Start Session:}\newline
        1. User clicks to start studying.\newline
        2. System initializes a new session ID and prepares memory context.\newline
        3. System returns the session ID to the client interface.\newline
        \textbf{End Session:}\newline
        4. User leaves the learning interface or clicks end session.\newline
        5. System clears the active session context from memory but retains history. \\
        \hline
        \textbf{Alternative Flow} & 
        \textbf{Session Timeout:}\newline
        A1. User is inactive for an extended period.\newline
        A2. System automatically ends the session and prompts the user to start a new one upon return. \\
        \hline
        \textbf{Exceptions} & If the session database fails to respond, gracefully fall back and notify the user to refresh the page. \\
        \hline
    \end{tabularx}
    \caption{Use case 3 Overview: Manage Learning Session}\label{tab:uc3}
\end{table}

\subsection{Use case 4: Ingest Course Material}
\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.5}
    \begin{tabularx}{\textwidth}{|l|X|}
        \hline
        \textbf{Use Case Name} & Ingest Course Material \\
        \hline
        \textbf{Actor} & Administrator / Instructor \\
        \hline
        \textbf{Description} & The actor uploads course slides and textbooks so the system can extract concepts and build the Educational Knowledge Graph. \\
        \hline
        \textbf{Preconditions} & The actor has valid administrative or instructional privileges.\newline
        The raw PDF files are accessible. \\
        \hline
        \textbf{Postconditions} & The knowledge base (Neo4j, Milvus) is populated with parsed nodes, embeddings, and relationships. \\
        \hline
        \textbf{Normal Flow} & 
        1. Actor submits the course name and target files via the ingestion endpoint.\newline
        2. System immediately returns a 200 SUCCESS status, indicating the task is running in the background.\newline
        3. System parses PDFs, segments windows, and extracts concepts (Dual-Phase Extraction).\newline
        4. System constructs the final Knowledge Graph and Vector store. \\
        \hline
        \textbf{Alternative Flow} & 
        \textbf{Invalid file format:}\newline
        A1. Actor uploads corrupted or unsupported file types.\newline
        A2. System aborts ingestion and logs an error without modifying the database. \\
        \hline
        \textbf{Exceptions} & If the LLM provider for extraction times out, the ingestion task pauses or retries based on internal middleware logic. \\
        \hline
    \end{tabularx}
    \caption{Use case 4 Overview: Ingest Course Material}\label{tab:uc4}
\end{table}

\subsection{Use case 5: Chat with TA Agent}
\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.5}
    \begin{tabularx}{\textwidth}{|l|X|}
        \hline
        \textbf{Use Case Name} & Chat with TA Agent \\
        \hline
        \textbf{Actor} & User (Student) \\
        \hline
        \textbf{Description} & The user submits a learning query to the AI Teaching Assistant and receives an educational response or pedagogical guidance. \\
        \hline
        \textbf{Preconditions} & The user is logged in and has an active session ID. \\
        \hline
        \textbf{Postconditions} & The user receives an appropriate textual answer, and UI actions (like PDF page scrolling) are triggered. \\
        \hline
        \textbf{Normal Flow} & 
        1. User submits a query (e.g., ``What is Machine Learning?'') in the chat interface.\newline
        2. System immediately accepts the request and returns a unique \texttt{task\_id}.\newline
        3. Client continuously polls the status of the \texttt{task\_id} in the background.\newline
        4. TA Agent orchestrates the response using the workflow (e.g., Teach, Retrieve, Roadmap).\newline
        5. Upon completion, the polling mechanism receives the final output (text and UI actions).\newline
        6. Client renders the response and updates the UI (e.g., highlights document). \\
        \hline
        \textbf{Alternative Flow} & 
        \textbf{TA Workflow Failure:}\newline
        A1. The TA agent encounters an internal error during orchestration.\newline
        A2. The polling endpoint returns a `Fail` status with error details.\newline
        A3. Client notifies the user that the TA encountered a problem. \\
        \hline
        \textbf{Exceptions} & Polling timeout: If the TA takes too long to respond (e.g., $>$ 300s), the client aborts polling and alerts the user. \\
        \hline
    \end{tabularx}
    \caption{Use case 5 Overview: Chat with TA Agent}\label{tab:uc5}
\end{table}
