\section*{Acknowledgement}
\thispagestyle{empty}
This section is dedicated to send my most sincere gratitute towards all who have played a role in the completion of this first phase of the thesis. Thanks to that, I was able to complete this thesis gracefully from requirement definitions to system research and development
\\\\
I would like to show my foremost appreciation to my supervisor, Mr.Thoai Nam for his unwavering support, guidance and constructive feedback. His expertise advice and guidance has really strengthened my vision and understanding, thus been instrumental in shaping the direction of my work.
\\\\
I am also greatly thankful to Computer Science Falcuty of Department for the learning environment, the facilities, the knowledge and the opportunity to orchestrate this work that I'm proud of. The contributions of my peers and colleagues in engaging discussions and shared insights have been enriching. 

To Bảo, a colleague and a friend of mine, whose knowledge and engaging discussion on system design has been a great help, I show my appreciation for his passionate and knowledgable share and consistent heart\-warming support.
\\\\
Finally, to all my friends and seniors who offered encouragement, shared their knowledge, giving inspiration and and especially those who shared years of teaching experience, your collective impact has been indispensible. This work stands firm on the contribution of all those mentioned above, and I are deeply appreciative of the roles each of you played in my orchestration.
\clearpage
\pagenumbering{arabic}
