\section*{Acknowledgement}
\thispagestyle{empty}
This section is dedicated to express our sincere gratitude towards all those who have played a crucial role in the
completion of the Specialized Project, also the first phase of the thesis. Your supports have been a great help for
me to perform various steps from the fundamental researches and requirement specification to system design and implementation
development, laying foundations for the future Capstone Project
\\\\
I would like to show my foremost appreciation to my supervisor, Mr.Thoai Nam for his unwavering support, guidance and constructive feedback. His invaluable expertise and advice has really strengthened my vision and understanding, thus been instrumental in shaping the direction of my work.
\\\\
I am also greatly thankful to Computer Science Falcuty of Department for the learning environment, the facilities, the knowledge and the opportunity to orchestrate this work that I'm proud of. The contributions of my peers and colleagues in engaging discussions and shared insights have been enriching. 

To Bảo, a colleague and a friend of mine, whose knowledge and engaging discussion on system design has been a great help, I show my appreciation for his passionate and knowledgable share and consistent heart\-warming support.
\\\\
Finally, to all my family and friends who offered encouragement, shared their knowledge and gave inspiration 
%and especially those who shared years of teaching assistant experience
, I feel blessed that this Project and me have been supported by your love and care. 
\\\\
Last but not least, I acknowledge that this my work would not achieve the goal without the foundation laid by pioneering researchers and engineers, both in the field of 
artificial intelligence and education. The theories, methodologies, and technologies they have developed have been the bedrock upon which this project is built. 
The knowledge they have contributed is invaluable, and I am more than honored to stand on the shoulders of giants.
\\\\
This work stands firm thanks to the contribution of all those mentioned above. Your accumulated impact has been indispensible, and I cherish the roles each played in this academic endeavor. 
\clearpage
\pagenumbering{arabic}
