\section*{Abstract}
\thispagestyle{empty}
Current world is changing at an incredible pace with constant information and knowledge update, while many educational systems remain stagnant. The rapid evolution of 
Artificial Intelligence has open doors for adaptive, self-directed learning online systems, replacing Learning Management Systems that offer static contents. 
However, common AI techniques such as Retrieval-Augmented Generation (RAG) struggle with static content, semantic fragmentation, and a lack of profound reasoning, while LLMs have limited 
context window and hallucination, inconsistent output.

To address these limitations, this project introduces \textbf{SmartEdu}, a proactive, mastery-oriented educational ecosystem powered by a graph-grounded multi-agent 
architecture.
By operating LLM on deterministic ingesting pipeline for academic materials, the system constructs an Automated Educational Knowledge Graph (EKG) that accurately 
maps conceptual hierarchies and prerequisite dependencies.  
Unstructured multimodal materials are automatically ingested via an asynchronous Producer-Consumer pipeline and processed through a novel Dual-Phase LLM extraction 
technique. This is reinforced by deterministic NLP filtering—including DBpedia validation and implicit clustering—to ensure strict ontological hierarchy and 
prerequisite acyclic constraints.

For real-time tutoring, a LangGraph-driven Teaching Assistant operates within an Adaptive Middleware harness, strictly separating reasoning contexts and action schemas. 
It utilizes Knowedge Graph as a well\-structured ground truth and solid reasoning frame, cooperates open-weights Small Language Models (SLMs) into workflow 
for localized and privacy-preserving execution, and
orchestrates specialized multi-agent workflows—Retrieve, Roadmap, and Teach—to perform dynamic student mastery tracking, automated gap detection
using topological algorithms, and personalized learning pathfinding, all while safeguarding student privacy and important resources through a robust 
Indentity-Session dynamic allocation and management.

Initial evaluations of the system demonstrate successful and consistent AI operations, effectively reduce hallucinations, produce consistent results and reasoning, and 
maintaining structural integrity across complex academic domains. Despite current latency bottlenecks and challenges in macro-level course pathing, 
SmartEdu establishes a robust, highly scalable foundation for shifting the educational paradigm from linear content delivery to interactive, 
human-like mentorship.

The project is being actively maintained on Github: \url{https://github.com/ttb-hcmut/SmartEdu}

\clearpage
\pagenumbering{arabic}
